---
title: "Hw2-Stat433"
author: "JakeReiners"
date: "9/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Q1.How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
```{r flights}
library(dplyr)

#install.packages("nycflights13")
library(nycflights13)
library(ggplot2)

sum(is.na(flights$dep_time))
## these are likely flights that were canceled. 

## to see the rest of how many each have NA:
summary(flights)

```
I would assume for the other NA's that they vary on reason. Having an Arrival Delay being NA to me could be cause the flight was canceled or diverted for example. 




Q2. Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
```{r q2}
dep_hour = flights$dep_time %/% 100
dep_minute = flights$dep_time %% 100
sched_dep_hour = flights$sched_dep_time %/% 100
sched_dep_minute = flights$sched_dep_time %% 100
flights$dep_time<- dep_hour*60 + dep_minute
flights$sched_dep_time <- sched_dep_hour*60 + sched_dep_minute
flights
```


q3Look at the number of canceled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point()

```{r q3}
by_day <- group_by(flights,year, month, day)
## why the difference?
summarise(by_day, delay = mean(dep_delay, na.rm = TRUE), canceled = sum(is.na(dep_delay))) %>%
  ggplot(aes(x=delay,y=canceled)) + geom_point()
```


